### 2014-11-13 tex/evaluation.tex
fixing the hash problem

>>>>

In summary, it appears that the benefits of avoiding
initialization-based nondeterminism more than outweigh the increased
complexity in the constraints. In fact, \symtxt{} can analyze certain
types of programs with orders of magnitude greater efficiency than
with \gsetxt{} or lazier\#, while covering exactly the same test cases
with zero loss of precision.
